---
title: "Raisin"
output: html_document
date: "2022-10-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Sources**

https://archive.ics.uci.edu/ml/datasets/Raisin+Dataset

**About**

Images of Kecimen and Besni raisin varieties grown in Turkey were obtained with CVS. A total of 900 raisin grains were used, including 450 pieces from both varieties. These images were subjected to various stages of pre-processing and 7 morphological features were extracted. These features have been classified using three different artificial intelligence techniques.

**Attribute Information:**

a)	ar: Area gives the number of pixels within the boundaries of the raisin.

b)	peri: Perimeter measures the environment by calculating the distance between the boundaries of the raisin and the pixels around it.

c)	majorAL: Major Axis Length gives the length of the main axis, which is the longest line that can be drawn on the raisin.

d)	minorAL: Minor Axis Length gives the length of the small axis, which is the shortest line that can be drawn on the raisin.

e)	ecc: Eccentricity gives a measure of the eccentricity of the ellipse, which has the same moments as raisins.

f)	conArea: Convex Area gives the number of pixels of the smallest convex shell of the region formed by the raisin.

g)	extent: Gives the ratio of the region formed by the raisin to the total pixels in the bounding box.

h)	class: Kecimen and Besni raisin.

**Contributors:**

Ilkay CINAR, Faculty of Technology, Selcuk University, Konya, TURKEY. ORCID ID : 0000-0003-0611-3316 ilkay.cinar ‘@’ selcuk.edu.tr

Murat KOKLU, Faculty of Technology, Selcuk University, Konya, TURKEY. ORCID ID : 0000-0002-2737-2360 mkoklu ‘@’ selcuk.edu.tr

Sakir TASDEMIR, Faculty of Technology, Selcuk University, Konya, TURKEY. ORCID ID : 0000-0002-2433-246X stasdemir ‘@’ selcuk.edu.tr

**Citation Request:**

CINAR I., KOKLU M. and TASDEMIR S., (2020), Classification of Raisin Grains Using Machine Vision and Artificial Intelligence Methods. Gazi Journal of Engineering Sciences, vol. 6, no. 3, pp. 200-209, December, 2020. DOI: https://doi.org/10.30855/gmbd.2020.03.03

## Attributes Details


```{r r1}
library(readxl)
library(moments)

raisin <- read_xlsx("Raisin.xlsx")
options(digits = 2)
summary(raisin)
```

**1) ar**

```{r r2,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
ar0<-class0$ar
hist(ar0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
ar1<-class1$ar
hist(ar1, main= "Histogram for class 1", col = "red")
ar<-raisin$ar
hist(ar, main= "Histogram for both classes", col = "green")
```

**2) peri**

```{r r3,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
peri0<-class0$peri
hist(peri0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
peri1<-class1$peri
hist(peri1, main= "Histogram for class 1", col = "red")
peri<-raisin$peri
hist(peri, main= "Histogram for both classes", col = "green")
```

**3) majorAL**

```{r r4,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
majal0<-class0$majorAL
hist(majal0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
majal1<-class1$majorAL
hist(majal1, main= "Histogram for class 1", col = "red")
majal<-raisin$majorAL
hist(majal, main= "Histogram for both classes", col = "green")
```

**4) minorAL**

```{r r5,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
minal0<-class0$minorAL
hist(ar0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
minal1<-class1$minorAL
hist(minal1, main= "Histogram for class 1", col = "red")
minal<-raisin$minorAL
hist(minal, main= "Histogram for both classes", col = "green")
```

**5) ecc**

```{r r6,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
ecc0<-class0$ecc
hist(ecc0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
ecc1<-class1$ecc
hist(ecc1, main= "Histogram for class 1", col = "red")
ecc<-raisin$ecc
hist(ecc, main= "Histogram for both classes", col = "green")
```

**6) conArea**

```{r r7,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
con0<-class0$conArea
hist(con0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
con1<-class1$conArea
hist(con1, main= "Histogram for class 1", col = "red")
con<-raisin$conArea
hist(con, main= "Histogram for both classes", col = "green")
```

**7) extent**

```{r r8,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(raisin,class=='Kecimen')
ex0<-class0$extent
hist(ex0, main= "Histogram for class 0", col = "blue")
class1<-subset(raisin,class=='Besni')
ex1<-class1$extent
hist(ex1, main= "Histogram for class 1", col = "red")
ex<-raisin$extent
hist(ex, main= "Histogram for both classes", col = "green")
```

## Correlation Matrix

**Class 0**

```{r}
options(digits = 2)
co0<-subset(raisin,class=='Kecimen')
cor(co0[-8])
det(cor(co0[-8]))
```

**Class 1**

```{r}
options(digits = 2)
co1<-subset(raisin,class=='Besni')
cor(co1[-8])
det(cor(co1[-8]))
```

**Both Classes**

```{r}
options(digits = 2)
cor(raisin[-8])
det(cor(raisin[-8]))
```